---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Connor Larson"
date: "8/28/2019"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

The datasaurus_dozen file has 1846 rows and 3 columns.

The variables included are: dataset, x, and y. 

### Exercise 2

Angry dino!

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:
(Probably not very good)

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
It's not very good!

### Exercise 3


A Star!

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The correlation doesn't look very good but let's get the data value anyways:

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

It's not good!

### Exercise 4

It's a circle!

```{r plot-circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

```{r cor-circle}

star_data %>%
  summarize(r = cor(x, y))
```

Another poor correlation.

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)